%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Curriculum Vitae
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%--------------------------------------------------------------------------------
% Header
%--------------------------------------------------------------------------------
\chapter*{Curriculum Vitae}
%\addcontentsline{toc}{chapter}{Curriculum Vitae}

% paragraph indention for the first line
\setlength{\parindent}{0em}
\newcommand{\tind}{\hspace{-\tabcolsep}}
\newcommand{\exrule}{\vspace{.2em}\hrule\vspace{.2em}}
\def\Cplusplus{{\rm C\raise.2ex\hbox{\small ++}}}
\sloppy

% paragraph spacing -- should be rubber length
\setlength{\parskip}{1.5em plus .5em minus .5em}

\parbox[t]{2.5cm}{\scshape Particulars}
\parbox[t]{12.5cm}{
  \begin{tabularx}{12.5cm}[t]{lX}
    \tind Date of Birth & 9th August 1975, Wittenberg, Germany\\
    \tind Nationality   & German, Swiss\\
    \tind Languages     & German (native), English (fluent), French (fluent)\\
    \tind Open Source Profile &
\htmladdnormallink{github.com/eile}{https://github.com/eile}\\
  \end{tabularx}
}\\

\parbox[t]{2.5cm}{\scshape Profile}
\parbox[t]{12.5cm}{Senior software engineer and technical team lead, with a
  specialization in interactive large data visualization, \Cplusplus, parallel
  and distributed programming. Successful track record of building and leading
  engineering teams to success.
}\\

\parbox[t]{2.5cm}{\scshape Expertise}
\parbox[t]{12.5cm}{
  Technical leadership for high performance C++ applications, parallel
    programming, distributed systems, Virtual Reality and collaborative
    visualization\vspace{.5em}\\
  Software and library design, test driven development and maintenance
    using \Cplusplus, Typescript, Python, CMake and git\vspace{.5em}\\
  Software development methodology during the whole lifecycle,
    ranging from requirements analysis, specification, design,
    implementation to documentation, education, debugging, optimization and
    support\vspace{.5em}\\
  Broad knowledge of operating systems: Mac OS X, Linux, Windows, Irix
}\\

\parbox[t]{2.5cm}{\scshape Experience}
\parbox[t]{12.5cm}{
  {\em Frontend Software Engineer} \hfill {\bf ESRI R\&D Center}\\
  Z{\"u}rich, Switzerland  \hfill {\bf Nov 2017 -- current}\exrule

  Development of frontend APIs and rendering algorithms for 3D mapping.}\\

\parbox[t]{2.5cm}{\hspace{1pt}}
\parbox[t]{12.5cm}{
  {\em Researcher, Parallel Rendering} \hfill {\bf University of Z"urich}\\
  Z"urich, Switzerland \hfill {\bf 2005 -- 2007, October 2015 -- current}\exrule

  Research new algorithms for large data visualization, in particular the
  parallelization, load-balancing and data distribution of parallel OpenGL
  applications on graphics clusters. Invented and developed Equalizer, a
  framework for scalable, distributed OpenGL applications.}\\

\parbox[t]{2.5cm}{\hspace{1pt}}
\parbox[t]{12.5cm}{
  {\em Visualization Team Manager} \hfill {\bf Blue Brain Project, EPFL}\\
  Lausanne, Switzerland  \hfill {\bf May 2011 -- Sep 2017}\exrule

  Built a team of seven software engineers, one post-doc, one PhD student and one
  media designer to deliver innovative visualization software as well as media
  for communication and scientific publications. Developed the long-term
  interactive supercomputing vision and the corresponding medium-term roadmap
  with the team, motivated and lead the implementation based on modular software
  components. Drove the implementation of software engineering best practices
  for the whole project.}\\

\parbox[t]{2.5cm}{\hspace{1pt}}
\parbox[t]{12.5cm}{
  {\em CEO and Founder} \hfill {\bf Eyescale Software GmbH}\\
  Neuch\^atel, Switzerland  \hfill {\bf January 2007 -- current}\exrule

  Co-founder of Eyescale and lead developer of the Equalizer parallel rendering
  framework and related libraries. Deploying Equalizer in existing ISV
  applications to scale display size, performance and visual quality. Software
  architecture, design and development, hardware and software consulting for
  multi-GPU workstations, visualization clusters and Virtual Reality.  }\\

\parbox[t]{2.5cm}{\hspace{1pt}}
\parbox[t]{12.5cm}{
  {\em Senior Software Engineer, 3D Graphics} \hfill {\bf Tungsten Graphics}\\
  Neuch\^atel, Switzerland  \hfill {\bf January 2007 -- June 2007}\exrule
  {\em Senior Software Engineer} \hfill {\bf Esmertec AG}\\
  Neuch\^atel, Switzerland  \hfill {\bf January 2004 -- September 2005}\exrule

  Job position details available on demand.
}\\

\parbox[t]{2.5cm}{\hspace{1pt}}
\parbox[t]{12.5cm}{
  {\em Senior Software Engineer}  \hfill {\bf Silicon Graphics, Inc.}\\
  Neuch\^atel, Switzerland \hfill {\bf August 2000 -- December 2003}\exrule

  Worked in SGI's advanced graphics division as technical lead for OpenGL
  Multipipe SDK (MPK), a framework to develop high performance, scalable
  visualization software. Worked on DataSync, a distributed shared memory API
  for clusters.  }\\

\parbox[t]{2.5cm}{\hspace{1pt}}
\parbox[t]{12.5cm}{
  {\em Software Engineer} \hfill {\bf Freelancer}\\
  Munich, Germany         \hfill {\bf April 2000 -- July 2000}\exrule
  {\em Software Engineer} \hfill {\bf Intec GmbH}\\
  Wessling, Germany       \hfill {\bf October 1998 -- March 2000}\exrule

  Job position details available on demand.
}\vspace{1em}\\

\parbox[t]{2.5cm}{\scshape Education}
\parbox[t]{12.5cm}{
  University of Zurich\\
  PhD in Computer Science, in progress
  \vspace{.3em}\\
  \`Ecole Polytechnique F\`ed\`erale de Lausanne\\
  Master in Computer Science, October 2015, Grade 5.6/6.0
  \vspace{.3em}\\
  Berufsakademie Heidenheim\\
  Dipl.-Ing. (eq BS) in Computer Science, September 1998
}\vspace{1em}\\

\nociteconf{EAA:17, SPEP:16, EDB:16, Hernando13, HBBES:13, EBAHMP:12, EEP:11, MEP:10, EP:07, BRE:05}
\bibliographystyleconf{apalike}
\bibliographyconf{references/references}                   % 'publications' is the name of a BibTeX file

\nocitejournal{ESP:18, EMP:09}
\bibliographystylejournal{apalike}
\bibliographyjournal{references/references}                   % 'publications' is the name of a BibTeX file
