%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abstract - English
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%--------------------------------------------------------------------------------
\chapter*{Abstract} \addcontentsline{toc}{chapter}{Abstract}
%--------------------------------------------------------------------------------
We are living in the big data age: An ever increasing amount of data is being
produced by users through data acquisition and computer simulations. While
large scale analysis and simulatons have received significant attention for
cloud computing and HPC systems, software to efficiently visualize large
amounts of data is struggling to keep up.

Visualization has proven to be an efficient tool for understanding data, in
particular visual analysis as a powerful tool to gain intuitive insight into the
spatial structure and relations of 3D data sets. Large-scale visualization
setups are becoming ever more affordable. High-resolution tiled display walls
are in reach even for small institutions, and can often be driven by a single
multi-GPU workstation. Virtual reality has arrived in the consumer space,
making it accessible for a large audience.

This thesis advances the field of parallel rendering by formalizing the design
and implementation of system software for large data visualization through
parallel rendering, novel algorithms to accelerate the rendering of large
amounts of data, and validates this research and development with new
applications for large data visualization. Our research and development enables
domain scientists and large data engineers to better extract meaning from their
data, making it feasible to explore more data by accelerating the rendering and
allowing the use of high-fidelity displays to see more detail.

